Methods to prioritise pop-up active transport infrastructure

### 2020-06-19 article.Rmd
Explain use of regions

<!-- The region of analysis may seem like a basic consideration: most cities have well-defined administrative zones. -->
<!-- In Leeds and many other cities, it makes sense to focus on the region directly surrounding the city centre, in a kind of 'geographical triage' to omit from the analysis pop-up options in the outskirts and focus valuable attention on the routes that are most likely to serve the highest number of people. -->
We set a modifiable parameter `city_centre_buffer_radius` with an initial value of 8 km (5 miles) to geographically subset potential routes. This represents a distance that most people have the physical ability to cycle.
Figure \@ref(fig:gsub) shows the result of subsetting based on physical distance from the centre vs plotting all possible transport network segments within the city boundaries. 
In some cases, regional geographies mean that roads close to an urban centre do not lie within the city boundaries.
<!-- could say more... -->

>>>>

The region of analysis may seem like a basic consideration: most cities have well-defined administrative zones.
In Leeds and many other cities, it makes sense to focus on the region directly surrounding the city centre, in a kind of 'geographical triage' to omit from the analysis pop-up options in the outskirts, focus valuable attention on the routes that are most likely to serve the highest number of people, and ensure that road sections outside administrative areas but close to key destinations are included.

<!-- The parameter `city_centre_buffer_radius` with an initial value of 8 km (5 miles) to geographically subset potential routes. -->
<!-- This represents a distance that most people have the physical ability to cycle. -->
Figure \@ref(fig:gsub) shows three broad strategies for geographic subsetting: based on administrative boundaries, distance from the centre, and distance from the centre and key destinations.
The latter case (Figure \@ref(fig:gsub), right) shows that administrative boundaries can exclude important roads.
The definition of 'city centres' and 'key destinations' is straightforward in clearly defined and well-understood city planning contexts.
In contexts where the method must be deployed nationwide, however the use of such subsetting approaches was found to be problematic, so the Rapid Cycleway Prioritisation Tool for England (v1) uses the first subsetting option, but subsets by larger regional boundaries to encourage regional collaboration on cycleway network design.
<!-- could say more... -->
